Classification of shapes

### 2019-09-05 manuscript/Manuscript2.Rnw
a few changes

\section{Missing Data}

Missing data problems arise in many statistical settings due to survey non-response (CITE), designed missingness in surveys \cite{LittleRhemtulla2013,WoodEtAl2018}, measurement error (CITE), and latent classes (CITE), to name a few examples.  There are numerous methods proposed in the literaure describing methods for handling missing data in a statistically principled manner.  For example, (Demspter Laird and Rubin) describes the EM algorithm for finding maximum likelihood estimates in the presence of missing data.  Another method, of particular interest in this setting, for handling mising data is multiple imputation \cite{LittleRubin1987,SchaferBook}.  The idea behind multiple imputation is to contruct a model for the missing values conditional on the observed values, and then fill in the missing values by randomly drawing from this distribution.  This process is repeated $M$ times to create $M$ completed data sets.  An analysis of interest is performed on each of the $M$ completed data sets (e.g. calculating a mean, multiple regression, clustering, etc.) and then the results are combined across the completed data sets using appropriate combining rules \cite{LittleRubin1987}.

For a more thorough review of the missing data literature, see \cite{HortonKleinman2007) (MORE).  
\section{Missing Data and Shapes}
Much of the research involving missing data in shape analysis has focused on work related to landmark based data \cite{GunzEtAl2009,GunzEtAl2004,NeeserEtAl2009, CouetteAndWhite2010}. By defining landmarks on each shape, the problem can be framed in a more traditional statistical setting where each landmark can be thought of as a variables and more traditional missing data techniques can be used.  
%\cite{GunzEtAl2009} presented a method for reconstructing hominin crania using landmarks and semi-landmarks.

@@

\cite{Robinson2012}: Partial shape matching paper at Florida State.

@@

A key ingredient in several classification methods (e.g. linear/quadratic discriminant analysis; kernel-based methods) for functional data is the notion of similarity or distance between curves. A popular choice is the distance induced by the $\mathbb{L}^2$ norm of a Hilbert space of square-integrable functions. However, it is well known that the $\mathbb{L}^2$ is unsuitable for comparing curves in the presence of parameterisation variability \citep{KurtekJASA, AK}. To this end we employ a suitable representation (transformation) of a curve $\C$ that allows us to compute distances easily while accounting for the necessary invariances.

@@

%Greg inserted this:
$\X(t)$ should be chosen from the distribution $\C_{mis}|\C_{obs}$.  In this case, this distribution will be approximated empirically.  To begin,  for a particular partially observed shape, $\C_j^p \in \mathbb{C}^p$, the distance between $\C_j^p$ and each of the completed shapes in $\C_i^f \in \mathbb{C}^f$ is computed. For a fixed $C_i^f \in \mathcal{C}^f$, for each $i=1,\ldots,n_f$ define the cost functional $\Phi_{\theta_j}:\mathcal{C}^p \times \mathcal{C}^f \to \mathbb{R}$ by

@@

or is scaling is desired

@@

We checked different values of M and k and included scaling vs not sclaing.

@@

\caption{Test}

@@

Classification is done using KNN, where the distances between the imputed tooth and the whole teeth are measured, and the most common class designation amongst the TEN ? teeth with the smallest distance measure is used to predict the class designation of the imputed tooth. A total of M of these predictions is then obtained based on the sampling from the K smallest distances earlier. Further, KNN classification based off the earlier, partial distances is used a means of assessing the performance of classifying based upon imputation. 
\subsection{Completing the curves}

@@

<<>>=
  for (tooth in c("LM1","LM2","LM3","UM1","UM2","UM3")){
  for (side in 1:2){print(c(tooth, side))
load(paste0("/Users/gregorymatthews/Dropbox/shapeanalysisgit/results/summaries/results20190610_side=",side,"_k=5_M=5_tooth=",tooth,"_summaries.RData"))

}}
@

\bibliography{shapebib}
\bibliographystyle{plainnat}

>>>>

\section{Missing Data}
Missing data problems arise in many statistical settings due to survey non-response (CITE), designed missingness in surveys \cite{LittleRhemtulla2013,WoodEtAl2018}, measurement error \cite{GuoHarelLittle2010}, and latent classes \cite{LCABook}, to name just a few examples.  There are numerous methods proposed in the literaure describing methods for handling missing data in a statistically principled manner.  For example, (Demspter Laird and Rubin) describes the EM algorithm for finding maximum likelihood estimates in the presence of missing data.  Another method, of particular interest in this setting, for handling mising data is multiple imputation \cite{LittleRubin1987,SchaferBook}.  The idea behind multiple imputation is to contruct a model for the missing values conditional on the observed values, and then fill in the missing values by randomly drawing from this distribution.  This process is repeated $M$ times to create $M$ completed data sets.  An analysis of interest is performed on each of the $M$ completed data sets (e.g. calculating a mean, multiple regression, clustering, etc.) and then the results are combined across the completed data sets using appropriate combining rules \cite{LittleRubin1987}.  For a full review of the missing data literature, see \cite{HortonKleinman2007, Murray2018}

\section{Missing Data and Shapes}
Work such as \cite{Brown2012} examines missing data in the morphology of crocodile skulls.  however, their data set consists of linear morphometric measurements of the skulls rather than dealing directly with the shape of th skull through landmarks or semi-landmarks.  Other research on missing data in shape analysis has focused on landmark based data such as \cite{GunzEtAl2009,GunzEtAl2004,NeeserEtAl2009,CouetteAndWhite2010}. By defining landmarks on each shape, the problem can be framed in a more traditional statistical setting where each landmark can be thought of as a covariate and more traditional missing data techniques, such as the EM algorithm and multiple imputation, can be used.  \cite{Arbour2014} look at four different methods for dealing with missing landmark data: Bayesian Principal Component Analysis (BPCA), least-squares regression, thin-plate splines (TPS), and mean substitution.  
%\cite{GunzEtAl2009} presented a method for reconstructing hominin crania using landmarks and semi-landmarks.

@@

The work most closely related to this current work can be found in \cite{Robinson2012}

Partial shape matching paper at Florida State.

@@

A key ingredient in several classification methods (e.g. linear/quadratic discriminant analysis; kernel-based methods) for functional data is the notion of similarity or distance between curves. A popular choice is the distance induced by the $\mathbb{L}^2$ norm of a Hilbert space of square-integrable functions. However, it is well known that the $\mathbb{L}^2$ is unsuitable for comparing curves in the presence of parameterisation variability \cite{KurtekJASA, AK}. To this end we employ a suitable representation (transformation) of a curve $\C$ that allows us to compute distances easily while accounting for the necessary invariances.

@@

%Greg inserted this:
$X(t)$ should be chosen from the distribution $C_{mis}|C_{obs}$.  In this case, this distribution will be approximated empirically.  To begin,  for a particular partially observed shape, $C_j^p \in \mathbb{C}^p$, the distance between $C_j^p$ and each of the completed shapes in $C_i^f \in \mathbb{C}^f$ is computed. For a fixed $C_i^f \in \mathcal{C}^f$, for each $i=1,\ldots,n_f$ define the cost functional $\Phi_{\theta_j}:\mathcal{C}^p \times \mathcal{C}^f \to \mathbb{R}$ by

@@

or if scaling is desired

@@

We checked different values of M and k and included scaling vs not scaling.

@@

\caption{An example of how the donor tooth is used to impute the donee}

@@

Classification is done using KNN, where the distances between the imputed tooth and the whole teeth are measured, and the most common class designation amongst the TEN ? teeth with the smallest distance measure is used to predict the class designation of the imputed tooth. A total of M of these predictions is then obtained based on the sampling from the K smallest distances earlier. Further, KNN classification based off the earlier, partial distances is used a means of assessing the performance of classifying based upon imputation.

\subsection{Completing the curves}

@@

\subsection{Tribe Classification}
Results of classification accuracy for tribe are presented using 1-nearest neighbor classification for values of $k$ (5, 10, and 20) and $M$ (5, 10, and 20) along with results when no imputation is used for classification.  Six different teeth are considered here (LM1, LM2, LM3, UM1, UM2, and UM3) along with two sides (1 (left) and 2 (right)).  
%Table \ref{tab:tribe:unscaled:accuracy} shows the accuracy of tribe classification when using size and shape for different imputation settings along with accuracy when using no imputation.  Table \ref{tab:tribe:scaled:accuracy} is similar to table \ref{tab:tribe:unscaled:accuracy}, except that only shape, as opposed to size and shape, is used to classify each tooth to a tribe.

  <<echo = FALSE>>=
 # res <- data.frame()
 # 
 # for (tooth in c("LM1","LM2","LM3","UM1","UM2","UM3")){
 #   for (side in 1:2){
 #     for (k in c(5,10,20)){
 #       for (M in c(5,10,20)){
 # try(load(paste0("/Users/gregorymatthews/Dropbox/shapeanalysisgit/results/summaries/results20190610_side=",side,"_k=",k,"_M=",M,"_tooth=",tooth,"_summaries.RData")))
 # 
 # res <- rbind(res,data.frame(tooth = tooth,side = side,k = k,M = M,accuracy_imputed = acc_imputed[1], accuracy_part = acc_part[1]))
 # 
 #       }}}}
 # 
 #   test <- rbind(
 #         c("LM1",1,round(res$accuracy_imputed[res$tooth=="LM1" & res$side == 1],3)),
 #         c("LM1",2,round(res$accuracy_imputed[res$tooth=="LM1" & res$side == 2],3)),
 #         c("LM2",1,round(res$accuracy_imputed[res$tooth=="LM2" & res$side == 1],3)),
 #         c("LM2",2,round(res$accuracy_imputed[res$tooth=="LM2" & res$side == 2],3)),
 #         c("LM3",1,round(res$accuracy_imputed[res$tooth=="LM3" & res$side == 1],3)),
 #         c("LM3",2,round(res$accuracy_imputed[res$tooth=="LM3" & res$side == 2],3)),
 #         c("UM1",1,round(res$accuracy_imputed[res$tooth=="UM1" & res$side == 1],3)),
 #         c("UM1",2,round(res$accuracy_imputed[res$tooth=="UM1" & res$side == 2],3)),
 #         c("UM2",1,round(res$accuracy_imputed[res$tooth=="UM2" & res$side == 1],3)),
 #         c("UM2",2,round(res$accuracy_imputed[res$tooth=="UM2" & res$side == 2],3)),
 #         c("UM3",1,round(res$accuracy_imputed[res$tooth=="UM3" & res$side == 1],3)),
 #         c("UM3",2,round(res$accuracy_imputed[res$tooth=="UM3" & res$side == 2],3))
 #         )
 # 
 #   test <- cbind(test,round(res$accuracy_part[seq(1,nrow(res),9)],3)[1:12])
 # 
 #   library(xtable)
 # addtorow <- list()
 # addtorow$pos <- list(0, 0)
 # addtorow$command <- c("& & \\multicolumn{3}{c}{k=5} & \\multicolumn{3}{c}{k=10} & \\multicolumn{3}{c}{k=20} & \\\\\n",
 # "Tooth & & Side & M=5 & M=10 & M=20 & M=5 & M=10 & M=20 & M=5 & M=10 & M=20 & Partial \\\\\n")
 # print(xtable(test), add.to.row = addtorow, include.colnames = FALSE, include.rownames = FALSE)
 @

% latex table generated in R 3.5.1 by xtable 1.8-2 package
% Mon Aug 26 14:31:26 2019
\begin{table}[ht]
\centering
\begin{tabular}{llllllllllll}
  \hline
  & & \multicolumn{3}{c}{k=5} & \multicolumn{3}{c}{k=10} & \multicolumn{3}{c}{k=20} & \\
 Tooth & Side & M=5 & M=10 & M=20 & M=5 & M=10 & M=20 & M=5 & M=10 & M=20 & Partial \\
 \hline
LM1 & 1 & 0.848 & 0.854 & 0.867 & 0.811 & 0.834 & 0.834 & 0.758 & 0.777 & 0.792 & 0.885 \\ 
  LM1 & 2 & 0.854 & 0.862 & 0.878 & 0.842 & 0.845 & 0.854 & 0.831 & 0.854 & 0.856 & 0.896 \\ 
  LM2 & 1 & 0.897 & 0.899 & 0.922 & 0.872 & 0.88 & 0.892 & 0.857 & 0.862 & 0.867 & 0.907 \\ 
  LM2 & 2 & 0.877 & 0.892 & 0.899 & 0.904 & 0.897 & 0.924 & 0.877 & 0.897 & 0.867 & 0.882 \\ 
  LM3 & 1 & 0.876 & 0.873 & 0.87 & 0.842 & 0.856 & 0.856 & 0.818 & 0.81 & 0.83 & 0.886 \\ 
  LM3 & 2 & 0.854 & 0.873 & 0.879 & 0.856 & 0.881 & 0.869 & 0.822 & 0.847 & 0.859 & 0.893 \\ 
  UM1 & 1 & 0.849 & 0.872 & 0.892 & 0.857 & 0.867 & 0.877 & 0.817 & 0.844 & 0.852 & 0.926 \\ 
  UM1 & 2 & 0.872 & 0.891 & 0.894 & 0.862 & 0.874 & 0.886 & 0.815 & 0.857 & 0.854 & 0.921 \\ 
  UM2 & 1 & 0.84 & 0.831 & 0.828 & 0.789 & 0.816 & 0.822 & 0.794 & 0.805 & 0.818 & 0.884 \\ 
  UM2 & 2 & 0.835 & 0.849 & 0.831 & 0.822 & 0.864 & 0.838 & 0.798 & 0.816 & 0.851 & 0.883 \\ 
  UM3 & 1 & 0.769 & 0.75 & 0.805 & 0.74 & 0.774 & 0.805 & 0.798 & 0.816 & 0.851 & 0.853 \\ 
  UM3 & 2 & 0.692 & 0.743 & 0.675 & 0.688 & 0.726 & 0.74 & 0.637 & 0.671 & 0.851 & 0.856 \\ 
   \hline
\end{tabular}
\caption{Tribe Classification of size and shape using nearest neighbor classification (i.e. k = 1)}
\label{tab:tribe:unscaled:accuracy}
\end{table}

<<echo = FALSE>>=
# res <- data.frame()
# 
# for (tooth in c("LM1","LM2","LM3","UM1","UM2","UM3")){
#   for (side in 1:2){
#     for (k in c(5,10,20)){
#       for (M in c(5,10,20)){
# try(load(paste0("/Users/gregorymatthews/Dropbox/shapeanalysisgit/results/summaries/results20190610_side=",side,"_k=",k,"_M=",M,"_tooth=",tooth,"scaled_summaries.RData")))
# 
# res <- rbind(res,data.frame(tooth = tooth,side = side,k = k,M = M,accuracy_imputed = acc_imputed[1], accuracy_part = acc_part[1]))
# 
#       }}}}
# 
#   test <- rbind(
#         c("LM1",1,round(res$accuracy_imputed[res$tooth=="LM1" & res$side == 1],3)),
#         c("LM1",2,round(res$accuracy_imputed[res$tooth=="LM1" & res$side == 2],3)),
#         c("LM2",1,round(res$accuracy_imputed[res$tooth=="LM2" & res$side == 1],3)),
#          c("LM2",2,round(res$accuracy_imputed[res$tooth=="LM2" & res$side == 2],3)),
#         c("LM3",1,round(res$accuracy_imputed[res$tooth=="LM3" & res$side == 1],3)),
#         c("LM3",2,round(res$accuracy_imputed[res$tooth=="LM3" & res$side == 2],3)),
#         c("UM1",1,round(res$accuracy_imputed[res$tooth=="UM1" & res$side == 1],3)),
#         c("UM1",2,round(res$accuracy_imputed[res$tooth=="UM1" & res$side == 2],3)),
#         c("UM2",1,round(res$accuracy_imputed[res$tooth=="UM2" & res$side == 1],3)),
#         c("UM2",2,round(res$accuracy_imputed[res$tooth=="UM2" & res$side == 2],3)),
#         c("UM3",1,round(res$accuracy_imputed[res$tooth=="UM3" & res$side == 1],3)),
#         c("UM3",2,round(res$accuracy_imputed[res$tooth=="UM3" & res$side == 2],3))
#         )
# 
#   test <- cbind(test,round(res$accuracy_part[seq(1,nrow(res),9)],3))
# 
#   library(xtable)
# addtorow <- list()
# addtorow$pos <- list(0, 0)
# addtorow$command <- c("& & \\multicolumn{3}{c}{k=5} & \\multicolumn{3}{c}{k=10} & \\multicolumn{3}{c}{k=20} &  \\\\\n",
# "Tooth & Side & M=5 & M=10 & M=20 & M=5 & M=10 & M=20 & M=5 & M=10 & M=20 & Partial  \\\\\n")
# print(xtable(test), add.to.row = addtorow, include.colnames = FALSE, include.rownames = FALSE)
@

% latex table generated in R 3.5.1 by xtable 1.8-2 package
% Fri Aug  9 13:39:28 2019
\begin{table}[ht]
\centering
\begin{tabular}{llllllllllll}
  \hline
  & & \multicolumn{3}{c}{k=5} & \multicolumn{3}{c}{k=10} & \multicolumn{3}{c}{k=20} &  \\
 Tooth & Side & M=5 & M=10 & M=20 & M=5 & M=10 & M=20 & M=5 & M=10 & M=20 & Partial  \\
 \hline
LM1 & 1 & 0.724 & 0.752 & 0.744 & 0.744 & 0.749 & 0.766 & 0.766 & 0.766 & 0.746 & 0.78 \\ 
  LM1 & 2 & 0.71 & 0.744 & 0.758 & 0.758 & 0.749 & 0.744 & 0.744 & 0.744 & 0.738 & 0.806 \\ 
  LM2 & 1 & 0.71 & 0.744 & 0.769 & 0.769 & 0.764 & 0.774 & 0.774 & 0.774 & 0.73 & 0.806 \\ 
  LM2 & 2 & 0.735 & 0.742 & 0.769 & 0.769 & 0.762 & 0.789 & 0.789 & 0.789 & 0.776 & 0.779 \\ 
  LM3 & 1 & 0.725 & 0.701 & 0.737 & 0.737 & 0.72 & 0.735 & 0.735 & 0.735 & 0.732 & 0.737 \\ 
  LM3 & 2 & 0.742 & 0.781 & 0.779 & 0.779 & 0.754 & 0.796 & 0.796 & 0.796 & 0.803 & 0.793 \\ 
  UM1 & 1 & 0.652 & 0.674 & 0.679 & 0.679 & 0.691 & 0.691 & 0.691 & 0.691 & 0.701 & 0.783 \\ 
  UM1 & 2 & 0.681 & 0.696 & 0.743 & 0.743 & 0.716 & 0.751 & 0.751 & 0.751 & 0.714 & 0.842 \\ 
  UM2 & 1 & 0.579 & 0.614 & 0.607 & 0.607 & 0.645 & 0.638 & 0.638 & 0.638 & 0.636 & 0.776 \\ 
  UM2 & 2 & 0.586 & 0.618 & 0.651 & 0.651 & 0.614 & 0.64 & 0.64 & 0.64 & 0.612 & 0.844 \\ 
  UM3 & 1 & 0.476 & 0.486 & 0.51 & 0.51 & 0.488 & 0.5 & 0.5 & 0.5 & 0.488 & 0.62 \\ 
  UM3 & 2 & 0.502 & 0.505 & 0.5 & 0.5 & 0.495 & 0.51 & 0.51 & 0.51 & 0.507 & 0.714 \\ 
   \hline
\end{tabular}
\caption{Tribe Classification using shape and nearest neighbor classification (i.e. k = 1)}
\label{tab:tribe:scaled:accuracy}
\end{table}

<<echo = FALSE>>=
 # tooth <- "LM1"
 # side <- 1
 #   library(ggplot2)
 # acc_res_list <- list()
 # for (tooth in c("LM1","LM2","LM3","UM1","UM2","UM3")){
 # #for (tooth in c("UM3")){
 #   for (side in 1:2){print(c(tooth, side))
 # load(paste0("/Users/gregorymatthews/Dropbox/shapeanalysisgit/results/summaries/results20190610_side=",side,"_k=5_M=5_tooth=",tooth,"_summaries.RData"))
 # acc_part_k5_M5 <- acc_part
 # acc_imputed_k5_M5 <- acc_imputed[1:20]
 #  rm(acc_part)
 # rm(acc_imputed)
 # 
 # load(paste0("/Users/gregorymatthews/Dropbox/shapeanalysisgit/results/summaries/results20190610_side=",side,"_k=5_M=10_tooth=",tooth,"_summaries.RData"))
 # acc_part_k5_M10 <- acc_part
 # acc_imputed_k5_M10 <- acc_imputed[1:20]
 # rm(acc_part)
 # rm(acc_imputed)
 # 
 # load(paste0("/Users/gregorymatthews/Dropbox/shapeanalysisgit/results/summaries/results20190610_side=",side,"_k=5_M=20_tooth=",tooth,"_summaries.RData"))
 # acc_part_k5_M20 <- acc_part
 # acc_imputed_k5_M20 <- acc_imputed[1:20]
 # rm(acc_part)
 # rm(acc_imputed)
 # 
 # load(paste0("/Users/gregorymatthews/Dropbox/shapeanalysisgit/results/summaries/results20190610_side=",side,"_k=10_M=5_tooth=",tooth,"_summaries.RData"))
 # acc_part_k10_M5 <- acc_part
 # acc_imputed_k10_M5 <- acc_imputed[1:20]
 # rm(acc_part)
 # rm(acc_imputed)
 # 
 # load(paste0("/Users/gregorymatthews/Dropbox/shapeanalysisgit/results/summaries/results20190610_side=",side,"_k=10_M=10_tooth=",tooth,"_summaries.RData"))
 # acc_part_k10_M10 <- acc_part
 # acc_imputed_k10_M10 <- acc_imputed[1:20]
 # rm(acc_part)
 # rm(acc_imputed)
 # 
 # load(paste0("/Users/gregorymatthews/Dropbox/shapeanalysisgit/results/summaries/results20190610_side=",side,"_k=10_M=20_tooth=",tooth,"_summaries.RData"))
 # acc_part_k10_M20 <- acc_part
 # acc_imputed_k10_M20 <- acc_imputed[1:20]
 # rm(acc_part)
 # rm(acc_imputed)
 # 
 # load(paste0("/Users/gregorymatthews/Dropbox/shapeanalysisgit/results/summaries/results20190610_side=",side,"_k=20_M=5_tooth=",tooth,"_summaries.RData"))
 # acc_part_k20_M5 <- acc_part
 # acc_imputed_k20_M5 <- acc_imputed[1:20]
 # rm(acc_part)
 # rm(acc_imputed)
 # 
 # load(paste0("/Users/gregorymatthews/Dropbox/shapeanalysisgit/results/summaries/results20190610_side=",side,"_k=20_M=10_tooth=",tooth,"_summaries.RData"))
 # acc_part_k20_M10 <- acc_part
 # acc_imputed_k20_M10 <- acc_imputed[1:20]
 # rm(acc_part)
 # rm(acc_imputed)
 # 
 # load(paste0("/Users/gregorymatthews/Dropbox/shapeanalysisgit/results/summaries/results20190610_side=",side,"_k=20_M=20_tooth=",tooth,"_summaries.RData"))
 # acc_part <- acc_part[1:20]
 # acc_imputed_k20_M20 <- acc_imputed[1:20]
 # 
 # dat <- data.frame(knn = rep(1:20,10), acc = c(acc_part,acc_imputed_k5_M5,acc_imputed_k5_M10,acc_imputed_k5_M20,acc_imputed_k10_M5,acc_imputed_k10_M10,acc_imputed_k10_M20,acc_imputed_k20_M5,acc_imputed_k20_M10,acc_imputed_k20_M20), k = c(rep("No Imp", 20), rep(c(5,10,20),each = 60)), M = c(rep("No Imp",20),rep(rep(c(5,10,20), each = 20),3)))
 # 
 # 
 # 
 # #dat <- data.frame(knn = rep(1:20,10), acc = c(acc_part,acc_imputed_k5_M5,acc_imputed_k5_M10,acc_imputed_k5_M20,acc_imputed_k10_M5,acc_imputed_k10_M10,acc_imputed_k10_M20,acc_imputed_k20_M5,acc_imputed_k20_M10,acc_imputed_k20_M20), type = rep(c("no imp","k5 M5","k5 M10","k5 M20","k10 M5","k10 M10", "k10 M20","k20 M5","k20 M10", "k20 M20"),each = 20))
 # 
 # dat$k <- factor(dat$k, levels = c("20", "10", "5", "No Imp"))
 # dat$M <- factor(dat$M, levels = c("20", "10", "5", "No Imp"))
 # 
 # library(ggplot2)
 # if(side == 1){
 # g1 <- ggplot(aes(x = knn, y = acc, colour = k, shape = M), data = dat) + geom_point() + geom_line() + ggtitle(paste0("tooth=",tooth,", side=",side)) + ylim(.6,.95) + theme(legend.position = "none")
 # }
 # 
 # if (side == 2){
 # g2 <- ggplot(aes(x = knn, y = acc, colour = k, shape = M), data = dat) + geom_point() + geom_line() + ggtitle(paste0("tooth=",tooth,", side=",side))  + ylim(.6,.95)
 # }
 # 
 # #print(c(mean(acc_imputed_20[1:20]),mean(acc_imputed_10[1:20]),mean(acc_imputed_5[1:20]),mean(acc_part_5[1:20])))
 # 
 # #acc_res_list[[paste0(tooth,"_",side)]] <- data.frame(accuracy  = c(mean(acc_imputed_20[1:20]),mean(acc_imputed_10[1:20]),mean(acc_imputed_5[1:20]),mean(acc_part_5[1:20])), tooth_type = rep(paste0(tooth,"_",side),4),  M_k = c("M20 l20", "M10 l10", "M5 l5", "No Imp"))
 # 
 #   }
 # 
 #   png(paste0("/Users/gregorymatthews/Dropbox/shapeanalysisgit/manuscript/fig/acc_by_tooth_by_knn_tribe_unscaled_",tooth,".png"), res = 300, units = "in", w = 8, h =4)
 #   library(gridExtra)
 # legend <- get_legend(g2)
 # g2 <- g2 + theme(legend.position="none")
 # grid.arrange(g1, g2, legend, ncol=3, widths=c(2.3, 2.3, 0.8))
 # dev.off()
 # 
 #   }

 # #dat <- do.call(rbind, acc_res_list)
 # #ggplot(aes(x = tooth, y = accuracy, col = M_k), data = dat) + geom_point()
 @

Tribe classification, Scaled results: 
<<echo = FALSE>>=
# tooth <- "LM1"
# side <- 1
#   library(ggplot2)
# acc_res_list <- list()
# for (tooth in c("LM1","LM2","LM3","UM1","UM2","UM3")){
# #for (tooth in c("LM1","LM2","LM3")){
#   for (side in 1:2){print(c(tooth, side))
# load(paste0("/Users/gregorymatthews/Dropbox/shapeanalysisgit/results/summaries/results20190610_side=",side,"_k=5_M=5_tooth=",tooth,"scaled_summaries.RData"))
# acc_part_k5_M5 <- acc_part
# acc_imputed_k5_M5 <- acc_imputed[1:20]
# rm(acc_part)
# rm(acc_imputed)
# 
# load(paste0("/Users/gregorymatthews/Dropbox/shapeanalysisgit/results/summaries/results20190610_side=",side,"_k=5_M=10_tooth=",tooth,"scaled_summaries.RData"))
# acc_part_k5_M10 <- acc_part
# acc_imputed_k5_M10 <- acc_imputed[1:20]
# rm(acc_part)
# rm(acc_imputed)
# 
# load(paste0("/Users/gregorymatthews/Dropbox/shapeanalysisgit/results/summaries/results20190610_side=",side,"_k=5_M=20_tooth=",tooth,"scaled_summaries.RData"))
# acc_part_k5_M20 <- acc_part
# acc_imputed_k5_M20 <- acc_imputed[1:20]
# rm(acc_part)
# rm(acc_imputed)
# 
# load(paste0("/Users/gregorymatthews/Dropbox/shapeanalysisgit/results/summaries/results20190610_side=",side,"_k=10_M=5_tooth=",tooth,"scaled_summaries.RData"))
# acc_part_k10_M5 <- acc_part
# acc_imputed_k10_M5 <- acc_imputed[1:20]
# rm(acc_part)
# rm(acc_imputed)
# 
# load(paste0("/Users/gregorymatthews/Dropbox/shapeanalysisgit/results/summaries/results20190610_side=",side,"_k=10_M=10_tooth=",tooth,"scaled_summaries.RData"))
# acc_part_k10_M10 <- acc_part
# acc_imputed_k10_M10 <- acc_imputed[1:20]
# rm(acc_part)
# rm(acc_imputed)
# 
# load(paste0("/Users/gregorymatthews/Dropbox/shapeanalysisgit/results/summaries/results20190610_side=",side,"_k=10_M=20_tooth=",tooth,"scaled_summaries.RData"))
# acc_part_k10_M20 <- acc_part
# acc_imputed_k10_M20 <- acc_imputed[1:20]
# rm(acc_part)
# rm(acc_imputed)
# 
# load(paste0("/Users/gregorymatthews/Dropbox/shapeanalysisgit/results/summaries/results20190610_side=",side,"_k=20_M=5_tooth=",tooth,"scaled_summaries.RData"))
# acc_part_k20_M5 <- acc_part
# acc_imputed_k20_M5 <- acc_imputed[1:20]
# rm(acc_part)
# rm(acc_imputed)
# 
# load(paste0("/Users/gregorymatthews/Dropbox/shapeanalysisgit/results/summaries/results20190610_side=",side,"_k=20_M=10_tooth=",tooth,"scaled_summaries.RData"))
# acc_part_k20_M10 <- acc_part
# acc_imputed_k20_M10 <- acc_imputed[1:20]
# rm(acc_part)
# rm(acc_imputed)
# 
# load(paste0("/Users/gregorymatthews/Dropbox/shapeanalysisgit/results/summaries/results20190610_side=",side,"_k=20_M=20_tooth=",tooth,"scaled_summaries.RData"))
# acc_part <- acc_part[1:20]
# acc_imputed_k20_M20 <- acc_imputed[1:20]
# 
# dat <- data.frame(knn = rep(1:20,10), acc = c(acc_part,acc_imputed_k5_M5,acc_imputed_k5_M10,acc_imputed_k5_M20,acc_imputed_k10_M5,acc_imputed_k10_M10,acc_imputed_k10_M20,acc_imputed_k20_M5,acc_imputed_k20_M10,acc_imputed_k20_M20), k = c(rep("No Imp", 20), rep(c(5,10,20),each = 60)), M = c(rep("No Imp",20),rep(rep(c(5,10,20), each = 20),3)))
# 
# #dat <- data.frame(knn = rep(1:20,10), acc = c(acc_part,acc_imputed_k5_M5,acc_imputed_k5_M10,acc_imputed_k5_M20,acc_imputed_k10_M5,acc_imputed_k10_M10,acc_imputed_k10_M20,acc_imputed_k20_M5,acc_imputed_k20_M10,acc_imputed_k20_M20), type = rep(c("no imp","k5 M5","k5 M10","k5 M20","k10 M5","k10 M10", "k10 M20","k20 M5","k20 M10", "k20 M20"),each = 20))
# 
# dat$k <- factor(dat$k, levels = c("20", "10", "5", "No Imp"))
# dat$M <- factor(dat$M, levels = c("20", "10", "5", "No Imp"))
# 
# library(ggplot2)
# if (side == 1){
# g1 <- ggplot(aes(x = knn, y = acc, colour = k, shape = M), data = dat) + geom_point() + geom_line() + ggtitle(paste0("tooth=",tooth,", side=",side)) + ylim(.4,.85) + theme(legend.position = "none")
# }
# 
# if (side == 2){
# g2 <- ggplot(aes(x = knn, y = acc, colour = k, shape = M), data = dat) + geom_point() + geom_line() + ggtitle(paste0("tooth=",tooth,", side=",side))  + ylim(.4,.85)
# }
# 
# 
# 
# 
# #print(c(mean(acc_imputed_20[1:20]),mean(acc_imputed_10[1:20]),mean(acc_imputed_5[1:20]),mean(acc_part_5[1:20])))
# 
# #acc_res_list[[paste0(tooth,"_",side)]] <- data.frame(accuracy  = c(mean(acc_imputed_20[1:20]),mean(acc_imputed_10[1:20]),mean(acc_imputed_5[1:20]),mean(acc_part_5[1:20])), tooth_type = rep(paste0(tooth,"_",side),4),  M_k = c("M20 l20", "M10 l10", "M5 l5", "No Imp"))
# 
#   }
# 
#     png(paste0("/Users/gregorymatthews/Dropbox/shapeanalysisgit/manuscript/fig/acc_by_tooth_by_knn_tribe_scaled_",tooth,".png"), res = 300, units = "in", w = 8, h =4)
# legend <- get_legend(g2)
# g2 <- g2 + theme(legend.position="none")
# grid.arrange(g1, g2, legend, ncol=3, widths=c(2.3, 2.3, 0.8))
#   dev.off()
# 
# 
#   }
# 
# 
# 
# 
# 
# #dat <- do.call(rbind, acc_res_list)
# #ggplot(aes(x = tooth, y = accuracy, col = M_k), data = dat) + geom_point()

 Tribe classification unscaled accuracy plot using knn = 1
 <<>>=
#    #tooth <- "LM1"
# #side <- 1
# library(ggplot2)
# acc_res_list <- list()
# for (tooth in c("LM1","LM2","LM3","UM1","UM2","UM3")){
#   for (side in 1:2){#print(c(tooth, side))
# load(paste0("/Users/gregorymatthews/Dropbox/shapeanalysisgit/results/summaries/results20190610_side=",side,"_k=5_M=5_tooth=",tooth,"_summaries.RData"))
# acc_part_k5_M5 <- acc_part
# acc_imputed_k5_M5 <- acc_imputed
# rm(acc_part)
# rm(acc_imputed)
# 
# load(paste0("/Users/gregorymatthews/Dropbox/shapeanalysisgit/results/summaries/results20190610_side=",side,"_k=5_M=10_tooth=",tooth,"_summaries.RData"))
# acc_part_k5_M10 <- acc_part
# acc_imputed_k5_M10 <- acc_imputed
# rm(acc_part)
# rm(acc_imputed)
# 
# load(paste0("/Users/gregorymatthews/Dropbox/shapeanalysisgit/results/summaries/results20190610_side=",side,"_k=5_M=20_tooth=",tooth,"_summaries.RData"))
# acc_part_k5_M20 <- acc_part
# acc_imputed_k5_M20 <- acc_imputed
# rm(acc_part)
# rm(acc_imputed)
# 
# load(paste0("/Users/gregorymatthews/Dropbox/shapeanalysisgit/results/summaries/results20190610_side=",side,"_k=10_M=5_tooth=",tooth,"_summaries.RData"))
# acc_part_k10_M5 <- acc_part
# acc_imputed_k10_M5 <- acc_imputed
# rm(acc_part)
# rm(acc_imputed)
# 
# load(paste0("/Users/gregorymatthews/Dropbox/shapeanalysisgit/results/summaries/results20190610_side=",side,"_k=10_M=10_tooth=",tooth,"_summaries.RData"))
# acc_part_k10_M10 <- acc_part
# acc_imputed_k10_M10 <- acc_imputed
# rm(acc_part)
# rm(acc_imputed)
# 
# load(paste0("/Users/gregorymatthews/Dropbox/shapeanalysisgit/results/summaries/results20190610_side=",side,"_k=10_M=20_tooth=",tooth,"_summaries.RData"))
# acc_part_k10_M20 <- acc_part
# acc_imputed_k10_M20 <- acc_imputed
# rm(acc_part)
# rm(acc_imputed)
# 
# load(paste0("/Users/gregorymatthews/Dropbox/shapeanalysisgit/results/summaries/results20190610_side=",side,"_k=20_M=5_tooth=",tooth,"_summaries.RData"))
# acc_part_k20_M5 <- acc_part
# acc_imputed_k20_M5 <- acc_imputed
# rm(acc_part)
# rm(acc_imputed)
# 
# load(paste0("/Users/gregorymatthews/Dropbox/shapeanalysisgit/results/summaries/results20190610_side=",side,"_k=20_M=10_tooth=",tooth,"_summaries.RData"))
# acc_part_k20_M10 <- acc_part
# acc_imputed_k20_M10 <- acc_imputed
# rm(acc_part)
# rm(acc_imputed)
# 
